# Post-Conf Questionnaire
Number of responses:
```{r echo = FALSE}
nrow(postconf)
```

## Personal details
We first would like to learn few personal details about you to be able to better interpret your answers in this questionnaire.

Note that these questions are the same as in the pre-conference questionnaire since we cannot correlate both questionnaires due to anonymity.

How many PAM conferences have you attended, including this one?
```{r echo = FALSE}
plotFactorDistribution(postconf, "numPAMs", "How many PAM conferences have you attended, including this one?")
```

In which timezone are you?

```
postconf$timezone <- recode(postconf$timezone,
       "(GMT -8:00) Pacific Time (US & Canada)" = "-8",
       "(GMT -7:00) Mountain Time (US & Canada)" = "-7",
       "(GMT -5:00) Eastern Time (US & Canada), Bogota, Lima" = "-5",
       "(GMT) Western Europe Time, London, Lisbon, Casablanca" = "+0",
       "(GMT +1:00) Brussels, Copenhagen, Madrid, Paris" = "+1",
       "(GMT +8:00) Beijing, Perth, Singapore, Hong Kong" = "+8"
)
```

```{r echo = FALSE}
plotFactorDistribution(postconf, "timezone", "In which timezone are you?")
```

From where are you participating in PAM?
```{r echo = FALSE}
plotFactorDistribution(postconf, "location", "From where are you participating in PAM?")
```

Please rate your professional seniority
```{r echo = FALSE}
plotFactorDistribution(postconf, "seniority", "Please rate your professional seniority")
```

Have you attended a remote conference before?
```{r echo = FALSE}
plotFactorDistribution(postconf, "priorRemoteExperience", "Please rate your professional seniority")
```

Would you have attended PAM as on-site conference in Oregon?
```{r echo = FALSE}
plotFactorDistribution(postconf, "visitOregon", "Would you have attended PAM as on-site conference in Oregon?")
```

## Overall Experience

This block is about assessing your overall experience of attending PAM as virtual conference. Did you enjoy it?

### Overall Experience
My overall experience of attending remotely PAM is
```{r echo = FALSE}
plotFactorDistribution(postconf, "overallExperience", "Overall Experience")
```

### Compared to attending on-site, attending remotely allowed me to better focus on the conference

I was more focused on the *technical content*
```{r echo = FALSE}
plotFactorDistribution(postconf, "focusOnContent", "I was more focused on the technical content")
```

I was more focused on *social interactions*
```{r echo = FALSE}
plotFactorDistribution(postconf, "focusOnInteractions", "I was more focused on social interactions")
```

### My expectations on attending a virtual conference were met

To present my work

```{r echo = FALSE}
plotFactorDistribution(postconf, "expectationPresentWork", "To present my work")
```

To follow presentations

```{r echo = FALSE}
plotFactorDistribution(postconf, "expectationFollowPresentations", "To follow presentations")
```

To interact with speakers

```{r echo = FALSE}
plotFactorDistribution(postconf, "expectationInteractWithSpeakers", "To interact with speakers")
```

To interact with participants

```{r echo = FALSE}
plotFactorDistribution(postconf, "expectationInteractWithParticipants", "To interact with participants")
```

### (optional) To speakers: My expectations on attending a virtual conference were met

This is a bug: the question was asked twice (mandatory above), optionally here.

To present my work

```{r echo = FALSE}
plotFactorDistribution(postconf, "expectationSpeakersPresentWork", "To present my work")
```

### Would you attend more conferences each year if they are offered online
```{r echo = FALSE}
plotFactorDistribution(postconf, "attendMoreConfsIfOnline", "Would you attend more conferences each year if they are offered online")
```

## Talk Sessions

In this section, we are interested how you experienced the talks sessions (i.e., paper and poster presentations).

### What tools did you use to participate in the conference and how well did they work?

```{r echo = FALSE}
plotFactorDistribution(postconf, "zoom", "Zoom")
```

```{r echo = FALSE}
plotFactorDistribution(postconf, "slack", "Slack")
```

### How do you rate the presentation sessions of this virtual conference compared to on-site conferences?

Ability to attend talks

```{r echo = FALSE}
plotFactorDistribution(postconf, "presentationsAttendTalks", "Ability to attend talks")
```

Ability to focus on the talks without distractions

```{r echo = FALSE}
plotFactorDistribution(postconf, "presentationDistractions", "Ability to focus on the talks without distractions")
```

Ability to ask questions

```{r echo = FALSE}
plotFactorDistribution(postconf, "askQuestions", "Ability to ask questions")
```

Ability to deeply discuss a topic openly with all participants

```{r echo = FALSE}
plotFactorDistribution(postconf, "discuss", "Ability to deeply discuss a topic openly with all participants")
```

### Did you experience video or audio degradations in Zoom?
```{r echo = FALSE}
plotFactorDistribution(postconf, "audioImpairments", "Audio Degradations")
```

```{r echo = FALSE}
plotFactorDistribution(postconf, "videoImpairments", "Video Degradations")
```

### Which one of the following factors during the online presentations affected your interest or ability to follow the talk or remain engage

Having a video of the speaker in the corner of slides

```{r echo = FALSE}
plotFactorDistribution(postconf, "speakerVideoOnSlides", "Having a video of the speaker in the corner of slides")
```

Presenter’s tone of speaking

```{r echo = FALSE}
plotFactorDistribution(postconf, "speakersToneOfSpeaking", "Presenter’s tone of speaking")
```

Changing of the audio across different segments of the presentation

```{r echo = FALSE}
plotFactorDistribution(postconf, "speakersAudioChange", "Changing of the audio across different segments of the presentation")
```

### Pros/Cons of pre-recorded talks

```{r echo = FALSE}
plotFactorDistribution(postconf, "prosConsPreRecordedTaks", "")
```

### (optional) Pros: What did you like about pre-recorded talks?
```{r echo = FALSE}
postconf$textProsPreRecordedTalks
```

### (optional) Cons: What did you not like about pre-recorded talks?
```{r echo = FALSE}
postconf$textConsPreRecordedTalks
```

### How many paper sessions did you skip due to time zone differences
```{r echo = FALSE}
plotFactorDistribution(postconf, "skippedSessions", "How many paper sessions did you skip due to time zone differences")
```

## Presentation-related Interactions

This section is about how you interacted with other participants about the content presented at the conference in terms of papers and posters.

### Did you participate in technical discussions on Slack or Zoom?
```{r echo = FALSE}
plotFactorDistribution(postconf, "participateSlackZoom", "Did you participate in technical discussions on Slack or Zoom?")
```

### How do you rate the interaction with others during this virtual conference compared to on-site conferences?
Ability to ask questions

```{r echo = FALSE}
plotFactorDistribution(postconf, "conferenceInteractionAskQuestions", "Ability to ask questions")
```

Moderation of questions by the session chairs when posting to the Zoom chat

```{r echo = FALSE}
plotFactorDistribution(postconf, "conferenceInteractionModeration", "Moderation of questions by the session chairs when posting to the Zoom chat")
```

Ability for detailed technical discussions

```{r echo = FALSE}
plotFactorDistribution(postconf, "conferenceInteractionDiscussion", "Ability for detailed technical discussions")
```

### With how many participants did you interact in *private* chats?

Slack private chats

```{r echo = FALSE}
plotFactorDistribution(postconf, "numberOfParticipantsSlackPrivateChat", "Slack private chats")
```

Zoom private chats

```{r echo = FALSE}
plotFactorDistribution(postconf, "numberOfParticipantsZoomPrivateChat", "Zoom private chats")
```

### (optional): Pros: Other feedback on *positive* aspects of the ability to interact during this virtual conference
```{r echo = FALSE}
postconf$textProsInteraction
```

### (optional): Cons: Other feedback on *negative* aspects of the ability to interact during this virtual conference

```{r echo = FALSE}
postconf$textConsInteraction
```

## Social Interactions (Virtual Hallway Track)
Besides content related to technical presentations (papers / posters), conferences are about general interactions with known and new researchers (e.g., during breaks or at the dinner table): the hallway track. We are interested in this section how you experienced the hallway track at PAM.

### Did you use Slack or the Zoom chat to interact with others about topics unrelated to the presentations?
```{r echo = FALSE}
plotFactorDistribution(postconf, "useSlackZoom", "")
```

### How do you rate the quality of social interactions (unrelated to the presentations) during this virtual conference compared to classical on-site conferences?
Interactions with researchers I already know

```{r echo = FALSE}
plotFactorDistribution(postconf, "hallwaytrackInteractionWithKnownResearchers", "Interactions with researchers I already know")
```

Interactions with new researchers I didn't know before

```{r echo = FALSE}
plotFactorDistribution(postconf, "hallwaytrackInteractionWithNewResearchers", "Interactions with new researchers I didn't know before")
```

### (optional) What did you enjoy about social interaction at this virtual conference?

```{r echo = FALSE}
postconf$textProsHallway
```

### (optional) How can social interactions be improved at virtual conferences?

```{r echo = FALSE}
postconf$textConsHallway
```

## General comments about remote attendance

### I would like to attend more virtual conferences in the future
```{r echo = FALSE}
plotFactorDistribution(postconf, "attendMoreVirtualConfsInFuture", "I would like to attend more virtual conferences in the future")
```

### How many venues should be virtual in the future?
```{r echo = FALSE}
plotFactorDistribution(postconf, "shareFutureVirtualConfs", "How many venues should be virtual in the future?")
```

### Net Promotor Score: How likely is it that you would recommend attending PAM as virtual conference to a colleague?
0 Not at all likely to recommend - 10 Extremely likely to recommend

```{r echo = FALSE}
plotFactorDistribution(postconf, "nps", "NPS")
```

### Pros: What worked well about attending remotely
```{r echo = FALSE}
postconf$textPros
```

### Cons: What did not work well about attending remotely
```{r echo = FALSE}
postconf$textCons
```

### Other comments / suggestions / feedback
```{r echo = FALSE}
postconf$textGeneralComments
```