# Pre-Conf Questionnaire

Number of responses:
```{r echo = FALSE}
nrow(preconf)
```

## Personal Details
How many PAM conferences have you attended, including this one?
```{r echo = FALSE}
plotFactorDistribution(preconf, "numPAMs", "How many PAM conferences have you attended, including this one?")
```

In which timezone are you?

```
preconf$timezone <- recode(preconf$timezone,
       "(GMT -8:00) Pacific Time (US & Canada)" = "-8",
       "(GMT -5:00) Eastern Time (US & Canada), Bogota, Lima" = "-5",
       "(GMT -4:00) Atlantic Time (Canada), Caracas, La Paz" = "-4",
       "(GMT +1:00) Brussels, Copenhagen, Madrid, Paris" = "+1",
       "(GMT +3:00) Baghdad, Riyadh, Moscow, St. Petersburg" = "+3",
       "(GMT +8:00) Beijing, Perth, Singapore, Hong Kong" = "+8"
)
```

```{r echo = FALSE}
plotFactorDistribution(preconf, "timezone", "In which timezone are you?")
```

From where are you participating in PAM?
```{r echo = FALSE}
plotFactorDistribution(preconf, "location", "From where are you participating in PAM?")
```

Please rate your professional seniority
```{r echo = FALSE}
plotFactorDistribution(preconf, "seniority", "Please rate your professional seniority")
```

Have you attended a remote conference before?
```{r echo = FALSE}
plotFactorDistribution(preconf, "priorRemoteExperience", "Please rate your professional seniority")
```

Would you have attended PAM as on-site conference in Oregon?
```{r echo = FALSE}
plotFactorDistribution(preconf, "visitOregon", "Would you have attended PAM as on-site conference in Oregon?")
```

## Planned participation

Do you intend to use the conference Slack/Zoom as virtual hallway track?
```{r echo = FALSE}
plotFactorDistribution(preconf, "intendedUseSlackZoomForHallwayTrack", "Do you intend to use the conference Slack/Zoom as virtual hallway track?")
```

In which sessions do you plan to participate?
```{r echo = FALSE}
plotFactorDistribution(preconf, "intendedSessionAttendance", "In which sessions do you plan to participate?")
```

Do you think you would attend more sessions if you would have attended PAM as on-site venue?
```{r echo = FALSE}
plotFactorDistribution(preconf, "attendMoreSessionsIfOnsite", "Do you think you would attend more sessions if you would have attended PAM as on-site venue?")
```

## Your goals when attending a on-site conference (e.g., prior editions of PAM)

To begin with, please tell us about your goals when attending an *on-site conference in person* (such as PAM in the previous years). We will ask you to your goals when attending PAM as online conference in the next section.

Importance of presenting my work to this community
```{r echo = FALSE}
plotFactorDistribution(preconf, "onsiteImportanceOfPresentingMyWork", "Importance of presenting my work to this community")
```

Importance of following paper/poster presentations
```{r echo = FALSE}
plotFactorDistribution(preconf, "onsiteImportanceOfPapers", "Importance of following paper/poster presentations")
```

Importance of interacting with other researchers I already know
```{r echo = FALSE}
plotFactorDistribution(preconf, "onsiteImportanceOfInteractingWithKnownResearchers", "Importance of interacting with other researchers I already know")
```

Importance of meeting new researchers
```{r echo = FALSE}
plotFactorDistribution(preconf, "onsiteImportanceOfMeetingNewResearchers", "Importance of meeting new researchers")
```

Importance of visiting the city/country in which the conference is held
```{r echo = FALSE}
plotFactorDistribution(preconf, "onsiteImportanceOfLocation", "onsite-importanceOfLocation")
```

## Your goals when attending PAM as virtual conference

Importance of presenting my work to this community
```{r echo = FALSE}
plotFactorDistribution(preconf, "virtualconfImportanceOfPresentingMyWork", "Importance of presenting my work to this community")
```

Importance of following paper/poster presentations
```{r echo = FALSE}
plotFactorDistribution(preconf, "virtualconfImportanceOfPapers", "Importance of following paper/poster presentations")
```

Importance of interacting with other researchers I already know
```{r echo = FALSE}
plotFactorDistribution(preconf, "virtualconfImportanceOfInteractingWithKnownResearchers", "Importance of interacting with other researchers I already know")
```

Importance of meeting new researchers
```{r echo = FALSE}
plotFactorDistribution(preconf, "virtualconfImportanceOfMeetingNewResearchers", "Importance of meeting new researchers")
```

## Other comments (optional)
Do you have other feedback / wishes / comments that you would like to share?
```{r rech = FALSE}
preconf$feedback
```